The eclipse of the V773 Tau B circumbinary disk

### 2022-06-16 src/tex/ms.tex
works locally but missing h5 data and image

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{@mkenworthy}

% Abstract with filler text
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
    Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
    Phasellus eu tellus sit amet tortor gravida placerat. 
    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
    Praesent eget sem vel leo ultrices bibendum. 
    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
    Curabitur auctor semper nulla donec varius orci eget risus. 
    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
    Duis eget orci sit amet orci dignissim rutrum.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
Phasellus eu tellus sit amet tortor gravida placerat. 
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
Praesent eget sem vel leo ultrices bibendum. 
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
Curabitur auctor semper nulla donec varius orci eget risus. 
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi. 
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae. 
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna. 
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante. 
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient. 
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis. 
Pellentesque cursus luctus mauris \citep{Luger2021}.

>>>>

%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
\documentclass{aa}  
\bibliographystyle{aa}

\usepackage{showyourwork}

\usepackage[nolist]{acronym}

\acrodef{vlba}[VLBA]{Very Long Baseline Array}

\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{natbib}
\usepackage{color}
\usepackage{hyperref}
\usepackage{nccmath}
\hypersetup{colorlinks=true,allcolors=[rgb]{0,0,0.8}}
% the three lines suppress the hyperref 'link empty' warnings
% explanation at: https://tex.stackexchange.com/questions/345764/journal-class-shows-package-hyperref-warning-suppressing-link-with-empty-targe
\makeatletter
\renewcommand*\aa@pageof{, page \thepage{} of \pageref*{LastPage}}

\newcommand{\rsun}{$R_{\odot}$}
\newcommand{\teff}{$T_{\rm eff}$}
\newcommand{\logg}{\ensuremath{\log g}}
\newcommand{\Msun}{$M_{\odot}$}
\newcommand{\logl}{log($L/L_{\odot}$)}
\def\kms{\ifmmode{\rm km\th s^{-1}}\else km\th s$^{-1}$\fi}
\def\th{\thinspace}

\newcommand\todo[1]{\colorbox{yellow}{\textcolor{red}{#1}}}
\newcommand{\RGM}[1]{\textcolor{cyan}{#1}}

\makeatother
%
\begin{document}

\title{The eclipse of the V773 Tau B circumbinary disk}

   \author{M.A. Kenworthy\inst{1}
          \and
          D. Gonz\'{a}lez Picos\inst{1}
          \and
          E. Elizondo\inst{2}
          \and
          R.G. Martin\inst{3}
          \and
          D.M. van Dam\inst{1}
          \and
          J.E. Rodriguez\inst{4}
          \and
          G.M. Kennedy\inst{5}
          \and
          C. Ginski\inst{1}
          \and
          M. Mugrauer\inst{6}
          \and
          N. Vogt\inst{7}
          \and 
          C. Adam\inst{8}
          \and
         R.J. Oelkers\inst{9}
}
   \institute{Leiden Observatory, University of Leiden,
   PO Box 9513, 2300 RA Leiden, The Netherlands\\
   \email{kenworthy@strw.leidenuniv.nl}
    \and
    Department of Physics and Astronomy, Wayne State University, 666 W Hancock St, Detroit, MI 48201, USA
    \and
    Department of Physics and Astronomy, University of Nevada, Las Vegas, 4505 South Maryland Parkway, NV 89154, USA
    \and 
    Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA
    \and
    Department of Physics, University of Warwick, Coventry CV4 7AL, UK
    \and
    Astrophysikalisches Institut und Universitäts-Sternwarte Jena, Schillergäßchen 2, D-07745 Jena, Germany
    \and
    Instituto de F\'{i}sica y Astronom\'{i}a, Facultad de Ciencias, Universidad de Valpara\'{i}so, Av. Gran Breta\~{n}a 1111, Playa Ancha, Valpara\'{i}so, Chile
\and
    Centro de Astronom\'ia (CITEVA), Universidad de Antofagasta, Avenida U. de Antofagasta, 02800, Antofagasta, Chile
    \and
    Munnerlyn Astronomical Instrumentation Laboratory, Department of Physics and Astronomy, Texas A\&M university, College Station, TX 77843 USA
    }

   \date{Received 2022-02-28; accepted 2022-06-14}

% \abstract{}{}{}{}{} 
% 5 {} token are mandatory

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {Young multiple stellar systems can host both circumstellar and circumbinary disks composed of gas and dust, and the orientations of circumbinary disks can be sculpted by the orientation and eccentricity of the central binaries.
   %
   Studying multiple binary systems and their associated disks enables understanding of the size and distribution of the planetary systems that subsequently form around them.}
  % aims heading (mandatory)
   {A deep ($\sim 70$\%) and extended ($\sim$150 days) eclipse was seen towards the young multiple stellar system V773 Tau in 2010.
   %
   We interpret it as due to the passage of a circumbinary disk around the B components moving in front of the A components.
   %
 Our aim is to characterise the orientation and structure of the disk, to refine the orbits of the subcomponents, and to predict when the next eclipse will occur.}
  % methods heading (mandatory)
   {We combine the photometry from several ground based surveys, construct a model for the light curve of the eclipse, and use high angular resolution imaging to refine the orbits of the three components of the system, A, B and C.
   %
   Frequency analysis of the light curves, including from the TESS satellite, enables characterisation of the rotational periods of the Aa and Ab stars.}
  % results heading (mandatory)
   {A toy model of the circumbinary disk shows that it extends out to approximately 5 au around the B binary and has an inclination of 73\degr{} with respect to the orbital plane of AB, where the lower bound of the radius of the disk is constrained by the geometry of the AB orbit and the upper bound is set by the stability of the disk.
   %
   We identify several frequencies in the photometric data that we attribute to rotational modulation of the Aa and Ab stellar companions.
   %
   We produce the first determination of the orbit of the more distant C component around the AB system and limit its inclination to 93\degr{}.
   %
}
  % conclusions heading (optional), leave it empty if necessary 
   {The high inclination and large diameter of the disk, together with the match from theory suggest that B is an almost equal mass, moderately eccentric binary.
   %
   We identify the rotational periods of the Aa and Ab stars, identify a third frequency in the light curve that we attribute to the orbital period of the stars in the B binary.
   %
   We predict that the next eclipse will be around 2037, during which both detailed photometric and spectroscopic monitoring will characterise the disk in greater detail.}

   \keywords{eclipses -- binaries: eclipsing}

   \maketitle
%
%________________________________________________________________

\section{Introduction}

Young multiple stellar systems are common \citep[e.g.][]{Ghez93,Duchene13} as are gas disks in and around the stellar components \citep{Akeson19}.
%
Chaotic accretion can occur during the star formation process as a result of turbulence within the molecular cloud from which the stars form \citep{Bate2003,McKee2007}.
%
Circumstellar and circumbinary disks can form with a misalignment to the binary orbital plane \citep{Monin2007, Bate2018}.

These binaries have been shown to influence and sculpt the circumbinary disks around them, possibly reinvigorating planet formation \citep{Cabrit06,Rodriguez18}.
%
%
The torque from a binary or multiple stellar system affects the formation and evolution of gas disks \citep[e.g.][]{Nelson2000, Mayer2005,Boss2006, Fu2017} and the interaction of planets with the disk \citep{Picogna2015,Lubow2016,Martin2016}.
%
Thus understanding how stellar multiplicity affects the formation and evolution of disks is important to explain observed exoplanet properties.

A misaligned circumbinary disk undergoes retrograde nodal precession.
%
If the binary is in a circular orbit, the precession is always around the binary angular momentum vector \citep[e.g.][]{Larwood1996}.
%
However, around an eccentric binary the precession is around the binary eccentricity vector if the initial misalignment is sufficiently high \citep{Farago2010,Aly2015}.
%
Dissipation within the disk causes the disk to align towards coplanar to the binary orbit, or polar to the binary orbit and aligned to the binary eccentricity vector \citep{Martin17,Lubow2018,Zanazzi2018}.
%
While all currently detected circumbinary planets are in coplanar orbits, around an eccentric binary polar planets may be more stable than coplanar planets \citep{Chen2020} and terrestrial planets at least form more efficiently \citep{Childs2021}.
%
If the disk lifetime is shorter than the disk alignment timescale then planets may form in misaligned orbits.

There are now many observations of circumbinary disks with a range of misalignment angles.
%
For example, KH~15D has a misalignment of about $3-15^\circ$ \citep{Chiang2004, Winn2004,Capelo2012,Poon2021}.
%
IRS~43 is misaligned by greater than $60^\circ$ \citep{Brinch16}, and the circumbinary disk around 99 Her has a polar misalignment \citep{Kennedy12}.
%
HD~98800 has a misalignment of $90^\circ$, meaning it is polar aligned to the central binary orbit \citep{Kennedy19,Zuniga-Fernandez21}.
%
Of the two possible disk inclinations allowed by observations, the polar alignment was first suggested by considering the dynamics of a disk since the polar alignment timescale is short compared to the stellar age.
%
Furthermore, the size of the inner hole in the disk that is carved by the binary orbit \citep{Artymowicz1994} is in agreement with a polar alignment \citep{Franchini19}.
%
There is also an external binary companion to the circumbinary disk in this system and its orbit is close to $34^\circ$ to the disk angular momentum.

V773 Tau is a young multiple stellar system that has been intensively studied as described in Section~\ref{sec:v773}.
%
It contains three components, each at a distinctly different stage of young stellar evolution - the A component is an almost equal mass binary, which in itself orbits around an almost equal mass B component that has an edge-on disk around it, forming a hierarchical multiple system with a decades long orbit.
%
Both these components are orbited by a third, C component that is highly embedded within a cloud of dust and is on a several hundred year orbit around both A and B.
%

In Section~\ref{sec:data} we present the photometry of the V773 system from several ground based surveys.
%
A deep extended eclipse occurs over a 200 day period, and we attribute this to a disk around the B component passing in front of the A components.
%
This disk is highly inclined with respect to the AB orbital plane, which should otherwise become coplanar within a dynamically short timescale.
%
Previous work \citep{Boden12} indicates that the B component is itself a tight, almost equal mass binary system.
%
If the B binary is also eccentric, then the disk will experience a torque that keeps it at the inclination that we observe.
%
Time series analysis of the photometry reveals two rotational periods consistent with the stars in the A binary, and a third period of approximately 67 days is revealed in the analysis.
%
If this period is attributed to the orbital period of the B binary, then we show that a moderate orbital eccentricity will keep the circumbinary disk at the observed inclination.
%
We derive the properties of the B binary and the circumbinary disk, and in Section~\ref{sec:orbitalfit} use the astrometry from the direct imaging observations to determine the expected epoch of the next eclipse of the A system.

Section~\ref{sec:variability} details our analysis of the photometric fluctuations due to both rotational modulation of Aa and Ab, and identifies a photometric signal whose period is a plausible measure of the orbit of the BaBb binary.
%
The long and extended eclipse is modeled in Section~\ref{sec:model} as an azimuthally symmetric dusty disk that is highly inclined to the AB orbital plane.
%
Theoretical consideration of the torques from an eccentric binary on a surrounding disk are discussed in Section~\ref{sec:theory} along with the prediction for the timing of the next eclipse in Section~\ref{sec:discuss}.
%
We summarise our results and discuss future observations in Section~\ref{sec:conclusions}.

\section{The V773 Tau system}\label{sec:v773}

\begin{figure}
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/v773_system_cartoon.pdf}
    \caption{Sketch of the V773 Tau system. 
    %
    We hypothesise that B is itself an equal mass binary system with a moderately eccentric orbit.
    %
    Orbits are not to scale.}
\label{fig:cartoon}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/v773tau_fig1.pdf}
    \caption{Optical photometry of the V773 Tau system.
    %
    The four different photometric surveys are represented by different colours, and each photometric series has been normalised using flux outside the main eclipse.
    %
    The inset panel shows the eclipse light curve in greater detail.
    %
    The PTF and KELT curves show different depths of the eclipse, indicating the presence of sub-micron dust that causes different amounts of optical extinction in the different pass bands of the two surveys.}
\label{fig:lc}
\end{center}
\end{figure*}

\subsection{Discovery and architecture}

V773 Tau (HD 283447, HBC 367) is a young \citep[$3\pm1$ Myr;][]{Boden07} stellar system that was identified as a young T Tauri star \citep{Rydgren76} and subsequently resolved as a visual double \citep{Ghez93,Leinert93}.
%
Its age was determined by comparing the temperature and luminosity of the stars Aa and Ab with PMS stellar models from \citet{Montalban06}, which show excellent consistency with the component parameters from \citet{Boden07}.
%
It is located at a distance of $132.8\pm 2.3 $ pc as determined by orbital and trigonometric parallax \citep{Torres12}, in contradiction with the larger distance determined by Gaia EDR3.
%
We attribute this discrepancy to the multiple source nature of the system which is not resolved by GAIA, and we use the distance determined by the spatially resolved A components with the VLA observations \citep{Torres12}.

The bound components of V773 Tau were initially identified as A, B and C (see Figure~\ref{fig:cartoon}).
%
The A component was resolved by \ac{vlba} observations to be a binary system with $P_{AaAb}=51.1003\pm 0.0022$ days and an eccentricity of $e=0.2710\pm 0.0072$ \citep{Torres12}.
%
The A binary becomes more luminous in radio waves during the periastron passage of the A stars, which is thought to be from the interacting magnetic fields of the two stars \citep{Torres12}.

A is orbited by the B component on a period of approximately 26 years, and both A and B are orbited by a C component with an orbital period of several hundred years \citep{Duchene03}.
%
C is a heavily reddened companion that is the faintest component at a wavelength of two microns but is the brightest at $4.7\mu m$ \citep{Duchene03,Woitas03}.
%
The flux contribution from C at optical wavelengths is approximately 100 times fainter than the A and B components \citep{Duchene03}.

\subsection{The B component}

Photometry of the B component shows a significantly greater amount of extinction compared to the A component, implying the presence of additional dust along the line of sight to the B component \citep{Torres12}.
%
The B component shows significant photometric variability on the order of 2 to 3 magnitudes in the $K$ band \citep{Boden12}, consistent with clouds or clumps of dust orbiting around the B component.
%
The initial fit to the spectral energy distribution (SED) suggested that the B component consisted of a single K star \citep{Duchene03}, but subsequent radial velocity monitoring and astrometry of the A binary enabled a dynamical mass determination of both the B and A components, revealing a much larger mass of $2.35 M_\odot$ for the B component \citep{Boden12}.
%
A single $2.35 M_\odot$ star would have a luminosity of $17 L_\odot$, inconsistent with the optical luminosity observed and the extinction derived.
%
If the B system is itself a binary, BaBb, then assuming equal mass components of $1.5 M_\odot$ yields a much lower luminosity that is consistent with the observed SED.
%
We therefore assume that the V773 Tau AB system is a hierarchical quadruple system, with a circumbinary disk around the B component which responsible for the significant reddening and photometric variability seen towards the B component.

% i_AaAb = 67.6+-1.5 degrees (Torres 2012)
% 
% i_AB = 71.48 +- 0.78 degrees (Boden 2012)

\section{Data}\label{sec:data}

\subsection{Discovery of the Eclipse with KELT}

The Kilodegree Extremely Little Telescope \citep[KELT; ][]{Pepper07,Pepper12, Pepper2018} survey is a project searching for transiting exoplanets, using two robotic wide-field telescopes, one at the Winer Observatory in Arizona (KELT-N) and the Southern African Astronomical Observatory (SAAO) near Sutherland (KELT-S).
%
The observatories consist of a $4096\times 4096$ AP16E Apogee CCD camera (KELT-N) and $4096\times 4096$ Alta U16M Apogee CCD camera (KELT-S) using a Kodak Wratten \#8 red-mass filter, comparable to an $R$ band magnitude.
%
The cameras are fed with a $f/19$ 42 mm (wide angle survey mode with 26\degr{}$\times$26\degr{} field of view) or a $f/28$ 200 mm (narrow angle campaign mode with 10.8\degr{}$\times$ 10.8\degr{} field of view) Mamiya lenses.
%
Images are obtained at a cadence of 10 to 30 minutes and yield useful magnitudes from 7 to 13.

% table
\begin{table*}
\caption{Orbital parameters for A and B systems. Data from \citet{Torres12} ``Joint solution'' for AaAb and from \citet{Boden12} for A-B. NOTE $\omega_A$ is defined in the RV sense for Torres and Boden, so that you will need to add 180\degr{} to $\omega_A$ for the Torres and Boden orbits to be correctly calculated in orbitize!}              % title of Table
\label{tab:orbs}      % is used to refer this table in the text
\centering                                      % used for centering table
\begin{tabular}{l c c c c}          % centered columns (4 columns)
\hline\hline                        % inserts double horizontal lines
Orbital  & Torres 2012  & Boden 2012    & this work   &  this work \\
 Parameter & AaAb  & AB    & AB   & AB-C  \\

\hline                                   % inserts single horizontal line
Period          & $51.1003\pm 0.0022$ d  & $26.20 \pm 1.1$  yr  &  $26.50  \pm 0.07$  yr  & $624_{-52}^{+83}$ yr\\
$T_0$           & $53059.92\pm 0.33$ (MJD) & $2010.53 \pm 1.0$ yr &  $2010.11\pm 0.12$  yr  & $1740_{-40}^{+26}$\\
$e$             & $0.2710\pm 0.0072$    & $0.099 \pm  0.026$ &  $0.104  \pm 0.009$    & $0.40_{-0.05}^{+0.04}$ \\
$\omega_A$ (deg)& $5.2\pm 2.7$          & $94 \pm 17$        &  $266.0 \pm 1.5$    & $107.8\pm 4.5$ \\
$\Omega$ (deg)  & $63.3\pm 1.1$         & $288.2 \pm 1.0$    &  $290.54 \pm 0.40$    & $104.6\pm 1.3$\\
$i$ (deg)       & $67.6\pm 1.5$         & $71.48 \pm 0.78$   &  $69.25 \pm 0.40 $    & $97.3\pm 0.6$\\
$a$ (mas)       & $2.837\pm 0.035$      & $115.5 \pm 3.4$    &  $117.7 \pm 0.86$    & $1013_{-74}^{+93}$\\
\hline                                             %inserts single line
\end{tabular}
\end{table*}

\begin{table}
\caption{Physical parameters for V773 Tau A-B. Data from \citet{Torres12} ``Joint solution'' for AaAb and from \citet{Boden12} for A-B}              % title of Table
\label{tab:physparams}      % is used to refer this table in the text
\centering                                      % used for centering table
\begin{tabular}{l c c}          % centered columns (4 columns)
\hline\hline                        % inserts double horizontal lines
Parameter & Value & Note \\
\hline                  % inserts single horizontal line
System distance (pc)        & $132.8 \pm 2.4$     & T2012 \\
A-subsystem mass ($M_\odot$)& $2.91 \pm 0.20$     & B2007; T2012 \\
A–B semimajor axis (AU)     & $15.35 \pm 0.45$    & B2012 \\
A–B system mass ($M_\odot$) & $5.27 \pm 0.65$     & B2012 \\
B mass ($M_\odot$)          & $2.35 \pm 0.67$     & B2012 \\
\hline                                             %inserts single line
\end{tabular}
\end{table}

The KELT survey has been highly successful in discovery and analysis of systems being eclipsed by circumstellar material, including the longest period eclipsing binary \citep{Rodriguez:2016}.
%
To search for eclipses of YSOs, we cross-matched the \citet{Zari2018} catalog of young stars in the solar neighbourhood that were identified by a combination of Gaia DR2 \citep{GaiaDR2} photometry and kinematics to the KELT catalog to obtain a sample of $\sim$1450 stars with lightcurves.
%
The corresponding KELT lightcurves for each YSO target were visually inspected for any large dimming events ($>$10\%) that lasted more than a week.
%
From this analysis, we identified a $\sim$80\% deep dimming event in V773 Tau, shown in Figure~\ref{fig:lc}.
%
The eclipse is incomplete, with the first half of the eclipse occurring when V773 Tau was behind the Sun, so we only observed the egress of the eclipse that lasted $\sim$100 days.
%
Based on this discovery, we searched for the eclipse in other photometric data sets.

\subsection{ASAS}

The All Sky Automated Survey \citep[ASAS; ][]{pojmanski_all_1997, asas_2005, asas_2018} is a survey consisting of two observing stations - one in Las
Campanas, Chile and the other on Maui, Hawaii. 
%
Each observatory is equipped with two CCD cameras using V and I filters and commercial f $ = 200$ mm, D $= 100$ mm lenses, although both larger (D $= 250$ mm) and smaller (50-72 mm) lenses were used at earlier times.
%
The majority of the data are taken with a pixel scale of $\approx$ 15\arcsec{}.
%
ASAS splits the sky into 709 partially overlapping (9\degr{} $\times$ 9\degr{} fields, taking on average 150 3-minute exposures per night, leading to a variable cadence of 0.3-2 frames per night.
%
Depending on the equipment used and the mode of operation, the ASAS limiting magnitude varied between 13.5 and 15.5 mag in V, and the saturation limit was 5.5 to 7.5 mag. 
%
Precision is around 0.01-0.02 mag for bright stars and below 0.3 mag for the fainter ones. 
%
ASAS photometry is calibrated against the Tycho catalog, and its accuracy is limited to 0.05 mag for bright, non-blended stars.

 \begin{table*}
\caption{Summary of the photometric data for V773 Tau employed in this work. Surveys with a * observed the eclipse. The start and end date are in HJD-2450000 format.}              % title of Table
\label{tab:v773tau_photometry}      % is used to refer this table in the text
\centering                                      % used for centering table
\begin{tabular}{l c c c}          % centered columns (4 columns)
\hline\hline                        % inserts double horizontal lines
Survey  & Start Date & End Date & N$_{\text{points}}$ \\
\hline                  % inserts single horizontal line
ASAS*              & 2621.65 &  8879.56& 712\\
SWASP  & 3215.71 & 4542.35 &  4902\\
HATNET    &4390.97 & 4552.81 & 3402\\
PTF*     & 5543.16 & 5782.49 & 121\\
ASAS-SN   & 5946.95 & 8451.85 & 882\\
KELT*   & 7020.84 & 2986.11 & 10272\\
ASAS-SN   & 8002.90 & 9488.90  & 1630\\
TESS      & 8816.10 & 8840.87 & 999\\
\hline
\end{tabular}
\end{table*}

\subsection{ASAS-SN}

The All Sky Automated Survey for Supernovae \citep[ASAS-SN; ][]{shappee_man_2014,kochanek_all-sky_2017} consists of six stations around the globe, with each station hosting four telescopes with a shared mount.
%
The telescopes consist of a 14-cm aperture telephoto lens with a field of view of approximately 4.5\degr{}$\times$4.5\degr{} and an 8.0\arcsec{} pixel scale.
% 
Two of the original stations (one in Hawaii and one in Chile) are fitted with $V$ band filters, whereas the other stations (Chile, Texas, South Africa and China) are fitted with $g$ band filters.
%
ASAS-SN observes the whole sky every night with a limiting magnitude of about 17 mag in the $V$ and $g$ bands.
%

\subsection{PTF}

The Palomar Transient Factory (PTF) is an automated wide field optical photometric survey described in \citet{Law09}.
%
It uses an 8.1 square degree camera with 101 megapixels at  1\arcsec\ sampling mounted on the 48 inch Samuel Oschin telescope at the Palomar Observatory.
%
Nearly all of the images are taken in one of two filters - Mould-$R$ and SDSS-$g'$, reaching $m_{g'}\approx 21.3$ and $m_R \approx 20.6$ in 60 s exposures.
%
Over 120 photometric observations were obtained using the $R$ band filter \citep{Ofek12}.

\subsection{TESS}

The Transiting Exoplanet Survey Satellite \citep[TESS; ][]{2015JATIS...1a4003R} is a satellite designed to survey for transiting exoplanets among the brightest and nearest stars over most of the sky.
%
The TESS satellite orbits the Earth every 13.7 days on a highly elliptical orbit, scanning a sector of the sky spanning 24\degr $\times$ 96\degr\ for a total of two orbits, before moving on to the next sector. 
%
It captures images at a 2 second (used for guiding), 20 seconds (for 1 000 bright asteroseismology targets), 120 seconds (for 200 000 stars that are likely planet hosts) and 30 minutes (full frame image) cadences.
%
The instrument consists of 4 CCDs each with a field of view of 24\degr$\times$24\degr, with a wide band-pass filter from 600-1000 nm (similar to the $I_C$ band) and has a limiting magnitude of about 14-15 mag ($I_C$).
%
The data was extracted from the TESS archive using the {\tt eleanor} package \citep{Feinstein19} which corrected for known systematics in the cameras and telescope.

\subsection{Combined light curve}

A summary of all the photometry obtained for V773 Tau is shown in Table~\ref{tab:v773tau_photometry}.
%
Photometric data from each survey is normalised to account for camera and instrumental throughput offsets.
%
The relative flux is computed for each subset of points, where the baseline is determined by ignoring in-eclipse data.
%
The data out of eclipse is resampled to 1-day bins to improve the signal-to-noise ratio and reduce the number of points for display and analysis.
%
Photometric outliers are removed by sigma-clipping on the flux and rejecting points with large photometric error values.
%
Further processing includes removing the rotational variability due to the presence of spots on the A components, which is removed for each survey by fitting a stellar variability model (see Section~\ref{sec:variability}).

The light curve of V773 Tau is shown in Figure~\ref{fig:lc} with the photometry from all four ground-based surveys.
%
The depth of the eclipse is approximately 80\% at MJD~55450, with an estimated full width at half minimum of approximately 100 days. 
%
The start of the eclipse was not observed due to the observing season for the star.
%
Three surveys show the eclipse, with the PTF survey showing a slightly shallower eclipse depth compared to the ASAS light curve.
%
The PTF observed V773 Tau in the $R$-band while ASAS observations were in the $V$-band, as a result there is a color depth difference due to the wavelength dependent nature of dust absorption, indicating sub-micron sized dust.
%
The data from TESS is shown in Figure~\ref{fig:tess_variability}.

\subsection{Adaptive optics imaging}\label{sec:di}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{figures/V773Tau-nocoro.pdf}
    \caption{SPHERE image of V773 Tau AB and C. The axes are centred on A, and B is not visible in this image, being under the first diffraction ring of the A component.
    %
    C is shown to the lower left of AB.
    %
    North is up and East to the left.}
    \label{fig:sphere}
\end{figure}

The V773 Tau system was observed with the SPHERE/IRDIS \citep[Infra-Red Dual Imaging and Spectrograph; ][]{Beuzit19,Dohlen08}, mounted at the Nasmyth platform of the Unit 3 telescope (UT3) at ESO's VLT on 2021 Oct 28 (MJD 59515).
%
The IRDIS camera was used to obtain 16 images with 16s integration in direct imaging mode with no coronagraphs for a total integration time of 256 seconds.
%
The astrometric PSF extraction was done by simultaneously fitting 2 elliptical Moffat functions to the flux image.
%
The official astrometric calibration for the $BB-K$ filter \citep{Maire16} was used to correct the observations.
%
The image was corrected for geometric distortions and the true north offset (see Figure~\ref{fig:sphere}).
%
For the parallactic angle the header values of the data were used. 
%
Four independent measurements of the PA and separation were made (left and right detector side, beginning and end of the sequence). 
%
The resultant position is listed in Table~\ref{tab:newastrom}.

\begin{table*}
\caption{Orbital measurements for A, B and C.}              % title of Table
\label{tab:newastrom}      % is used to refer this table in the text
\centering                                      % used for centering table
\begin{tabular}{l c c c c c c c c}          % centered columns (4 columns)
\hline\hline
 &     $\theta(AB)$ & $\sigma_{\theta(AB)}$ & $\rho(AB)$ & $\sigma_{\rho(AB)}$ & $\theta(AC)$ & $\sigma_{\theta(AC)}$ & $\rho(AC)$ & $\sigma_{\rho(AC)}$ \\
    &     ($\degr$) & ($\degr$)             & (mas)      & (mas)               & ($\degr$)    & ($\degr$)             & (mas)      & (mas)               \\
\hline
Moffat fit &     -- &                --     &   --       &  --                 & 139.94          & 1.1                   & 264.6      & 6.8                 \\
Orbitize!  &  339.1 & 0.5                   & 73.8       & 0.6                 & 139.92          & 0.04                  & 262.05     & 0.28                \\
\hline
\end{tabular}
\end{table*}

To confirm the astrometry of AC and to measure the AB separation in the presence of A's diffraction rings, a custom fitting routine was used.
%
The centre of A and C was determined by choosing a trial value for the $(x,y)$ position of the light centroid of the stellar PSF, then rotating by 180\degr{} and subtracting this image from the unrotated image.
%
The  {\tt emcee} package \citep{foreman-mackey2013} was then used to minimise the calculated $\chi^2$ of the residuals within a disk with diameter equal to the Airy disk of the PSF centered on the trial coordinates, and the pixel positions along with the errors derived through marginalisation of the distributions was calculated.

\begin{figure}
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/astrometry_ABC.pdf}
    \caption{Determining the astrometry of V773 Tau A, B and C.
    %
    The left hand panel shows the rotation subtracted image of the V773 system, which was constructed by rotating the image by 180 degrees around the centroid of A (indicated by the red dot), then subtracting it from the original image.
    %
    The positive flux image of C is seen to the lower left and the negative flux image of C to the upper right.
    %
    The positive flux image of the B component is then seen to the upper right of the centroid of A, indicating its location.
    %
    The right hand panel shows the subtraction of the positive image of C from the location of B, with B marked with a red circle.
    %
    Residuals from the subtraction processes can be seen around the location of A and B.}
  \label{fig:rotsub}
  \script{make_astrometry_ABC_plot.py}
\end{center}
\end{figure}

With the centroid of star A determined, we then subtracted a 180 degree rotated image of A from the original image, revealing the B system at the location of the first diffraction ring of system A (see Figure~\ref{fig:rotsub} left panel).
%
We then use star C as a reference PSF, translate it to the location of B, scale the flux of the image by a factor $f$ and then use {\tt emcee} to determine the relative separation of B and C (see Figure~\ref{fig:rotsub} right panel).
%
With the absolute pixel positions of A and C, the relative position of B with respect to C and the pixel scale of the SPHERE IRDIS camera, the position angles and separations of AB and AC are determined. 
%
The AC values are found to be consistent with the Moffat fitting procedure for AC and all fitting results are listed in Table~\ref{tab:newastrom}.

Errors reported on the astrometry using {\tt emcee} are smaller than those reported in previous measurements on larger telescopes, even though our signal to noise is similar.
%
The fitting routine does not include systematic errors, which are difficult to quantify with the diffraction ring residuals seen at the location of the B component.
%
We therefore doubled the errors on the measured relative position of A from B, which is consistent with the errors reported by other papers, to represent the systematic errors in our fitting.

\section{Orbital fitting for A, B and C}\label{sec:orbitalfit}

\begin{figure*}[ht]
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/v773_tau_b_orbits-long_burn.pdf}
        \caption{The orbit of the V773 Tau AB system.
        %
        A is fixed at the origin in the left hand panel.
        %
        The right hand panels show the separation and position angles of the astrometry.}
\label{fig:v773orbitize}
\end{center}
\end{figure*}

\begin{figure*}[ht]
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/v773_tau_c_orbits-long_burn.pdf}
        \caption{The orbit of the V773 Tau C system.
        %
        The barycentre of AB is fixed at the origin in the left hand panel.
        %
        The right hand panels show the separation and position angles of the astrometry.}
\label{fig:v773Corbitize}
\end{center}
\end{figure*}

We combined previously obtained astrometry of the V773 Tau system \citep[from the analysis of ][]{Duchene03,Boden12} with our reported astrometry, and used the {\tt orbitize!} \citep{Blunt20,foreman-mackey2013} package to perform an updated orbital fit for the AB system and the orbit of C around the barycentre of AB.
%
For {\tt orbitize!} we use 1000 walkers, the number of temperatures is 20 (to move walkers out of local minima in the optimization function), a burn in of 2000 per walker and a total run of $10^6$ steps for both systems.
%
The output is in the form of orbits (consisting of six orbital elements, the total mass of the system and the parallax) with fits consistent with the astrometry, which are referred to as a `bundle'.
%
By marginalising over all the other orbital parameters in the bundle, a distribution for each orbital parameter is constructed.
%
The value and quoted errors for the orbital elements are at the 16th, 50th and 84th percentile points of each distribution, and show no significant correlation for the AB system, indicating a good orbital fit.
%
The orbital elements of the AB system are shown in Table~\ref{tab:orbs}.

With the updated orbital bundles generated for the AB system, we then took the measured AC astrometry as reported in Table 1 of \citet{Duchene03} and Table 1 of \citet{Boden12} and combined it with the 2021 astrometry.
%
We then corrected the AC relative astrometry using the measured masses of A and B and calculated the distance from C to the the barycenter of AB (called C-AB).
%
Using the C-AB astrometry, we carried out an {\tt orbitize!} fit with parameters identical to that of the AB system.
%
The orbital period of C around the AB system is on the order of hundreds of years, and so only a short arc of the orbit is traced out across the observed epochs.
%
The resultant orbital bundle shows a much wider spread of orbital parameters, ranging from periods of several decades to almost a thousand years.
%
The orbital bundle includes the combined mass of AB and C, including some unphysically low masses, so we keep bundles with masses between 3.5 and 7.0 $M_\odot$.
